Differences in care for patients experiencing left vs. right hemisphere ICH

### 2024-02-13 reports/aggressiveness.qmd
dags

library(targets)
library(readr)
library(tidyr)
library(skimr)
library(dplyr)
library(gt)
library(gtsummary)
library(ggplot2)
library(marginaleffects)
library(modelsummary)

@@

tar_load(ich)
tar_load(non_surgery_trials)
tar_load(surgery_trials)
tar_load(table_1)
tar_load(table_2)

@@

>>>>

library(targets)
library(readr)
library(tidyr)
library(skimr)
library(dplyr)
library(gt)
library(gtsummary)
library(ggplot2)
library(ggdag)
library(dagitty)
library(marginaleffects)
library(modelsummary)

@@

# tar_load(ich)
# tar_load(non_surgery_trials)
# tar_load(surgery_trials)
# tar_load(table_1)
# tar_load(table_2)
# tar_load(aggressive_dag)
tar_load_everything()

@@

```{r}
#| width: 1200
#| height: 2000
#| fig-align: center
#|
theme_set(
  theme_dag() %+replace%
    # also add some additional styling
    theme(
      legend.position = "bottom",
      strip.text.x = element_text(margin = margin(2, 0, 2, 0, "mm"))
    )
)

ggdag_adjustment_set(aggressive_dag, shadow = TRUE, use_labels = "label", text = FALSE)

ggdag_adjustment_set(outcome_dag, shadow = TRUE, use_labels = "label", text = FALSE)

aggressive_dag |>
  ggdag_paths(shadow = TRUE, text = FALSE, use_labels = "label")
